A dynamic bioenergetic model for coral-\emph{Symbiodinium} symbioses and coral bleaching as an alternate stable state

### 2017-03-26 ms/ms.tex
update filenames
update links

  \title{A dynamic bioenergetic model for coral-\emph{Symbiodinium} symbioses and
coral bleaching as an alternate stable state}
    \author[University of Hawaii]{Ross Cunning\corref{c1}}
   \ead{ross.cunning@gmail.com} 
   \cortext[c1]{Corresponding Author}
    \author[UCSB, MSI]{Erik B. Muller}

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \emph{Develop a new module of photo-oxidative stress.} Of primary
  interest to coral biologists and ecologists is symbiosis dysfunction
  under environmental stress, resulting in coral ``bleaching''--the loss
  of algal symbionts from the association (Jokiel and Coles 1977).
  Bleaching is thought to be triggered by photo-oxidative stress in
  \emph{Symbiodinium} (Weis 2008), which has been modeled previously as
  a response to absolute external irradiance (Eynaud, Nisbet, and Muller
  2011). However, this response may also depend on self-shading by other
  symbionts (Enríquez, Méndez, and Iglesias-Prieto 2005),
  CO\textsubscript{2} availability at the site of photosynthesis
  (Wooldridge 2009), and other non-photochemical quenching mechanisms
  (Roth 2014). We incorporate these features into a new photo-oxidative
  stress module linking overreduction of the photosynthetic light
  reactions to downstream impacts of photoinhibition and photodamage.
  Importantly, this formulation introduces a link between
  CO\textsubscript{2}-limitation of photosynthesis and bleaching, and
  potential synergistic roles for heterotrophy and nutrient availability
  in influencing bleaching responses (Wooldridge 2014b)
\item
  \emph{Reduce theoretical and mathematical complexity.} Following the
  logic of Jager, Martin, and Zimmer (2013), we exclude certain features
  of formal DEB theory in order to capture behaviors of interest with
  the simplest possible formulation. Here, we present a model without
  reserves, maturity, or reproduction (see Kooijman 2010). This
  formulation precludes modeling the full life cycle of corals as
  reproduction, larval stages, and metamorphosis are not considered, but
  greatly reduces theoretical complexity and parameter numbers, which is
  advantageous given the relative paucity of data for corals. Moreover,
  dynamics of the symbiosis (i.e., changes in symbiont to host biomass,
  including bleaching and recovery) and coral biomass growth are
  efficiently captured with this simpler formulation, which also
  increases accessibility for biologists and ecologists without
  requiring expertise in DEB theory.
\item
  \emph{Provide well-documented, open source code.} In order to
  facilitate the continued development and application of theoretical
  modeling tools for coral symbioses, we provide open access to the
  model in the form of detailed, commented code written in the R
  language (R Core Team 2014). With an accessible and modular framework,
  we envision this model as a resource for further development by the
  scientific community to include additional complexity and
  problem-specific components. We chose R, an open source programming
  language in common use by biologists and ecologists, to reach the
  widest possible audience with this work.
\end{enumerate}

@@

\begin{longtable}[c]{@{}llll@{}}

@@

\begin{minipage}[b]{0.10\columnwidth}\raggedright\strut
Symbol
\strut\end{minipage} &
\begin{minipage}[b]{0.45\columnwidth}\raggedright\strut
Description
\strut\end{minipage} &
\begin{minipage}[b]{0.27\columnwidth}\raggedright\strut
Units
\strut\end{minipage} &
\begin{minipage}[b]{0.10\columnwidth}\raggedright\strut
Eq. no.
\strut\end{minipage}\tabularnewline

@@

\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
\(j_X\)
\strut\end{minipage} &
\begin{minipage}[t]{0.45\columnwidth}\raggedright\strut
Prey assimilation (feeding) rate
\strut\end{minipage} &
\begin{minipage}[t]{0.27\columnwidth}\raggedright\strut
C-mol X C-mol H\textsuperscript{-1} d\textsuperscript{-1}
\strut\end{minipage} &
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
3
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
\(j_N\)
\strut\end{minipage} &
\begin{minipage}[t]{0.45\columnwidth}\raggedright\strut
Nitrogen uptake rate
\strut\end{minipage} &
\begin{minipage}[t]{0.27\columnwidth}\raggedright\strut
mol N Cmol H\textsuperscript{-1} d\textsuperscript{-1}
\strut\end{minipage} &
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
4
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
\(j_{HG}\)
\strut\end{minipage} &
\begin{minipage}[t]{0.45\columnwidth}\raggedright\strut
Host biomass formation rate
\strut\end{minipage} &
\begin{minipage}[t]{0.27\columnwidth}\raggedright\strut
C-mol H C-mol H\textsuperscript{-1} d\textsuperscript{-1}
\strut\end{minipage} &
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
5
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
\(j_{HT}\)
\strut\end{minipage} &
\begin{minipage}[t]{0.45\columnwidth}\raggedright\strut
Host biomass turnover rate
\strut\end{minipage} &
\begin{minipage}[t]{0.27\columnwidth}\raggedright\strut
C-mol H C-mol H\textsuperscript{-1} d\textsuperscript{-1}
\strut\end{minipage} &
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
6
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
\(r_{NH}\)
\strut\end{minipage} &
\begin{minipage}[t]{0.45\columnwidth}\raggedright\strut
Recycled nitrogen from host turnover
\strut\end{minipage} &
\begin{minipage}[t]{0.27\columnwidth}\raggedright\strut
mol N C-mol H\textsuperscript{-1} d\textsuperscript{-1}
\strut\end{minipage} &
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
7
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
\(\rho_N\)
\strut\end{minipage} &
\begin{minipage}[t]{0.45\columnwidth}\raggedright\strut
Nitrogen shared with the symbiont
\strut\end{minipage} &
\begin{minipage}[t]{0.27\columnwidth}\raggedright\strut
mol N C-mol H\textsuperscript{-1} d\textsuperscript{-1}
\strut\end{minipage} &
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
8
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
\(j_{eC}\)
\strut\end{minipage} &
\begin{minipage}[t]{0.45\columnwidth}\raggedright\strut
Excess carbon used to activate host CCMs
\strut\end{minipage} &
\begin{minipage}[t]{0.27\columnwidth}\raggedright\strut
mol C C-mol H\textsuperscript{-1} d\textsuperscript{-1}
\strut\end{minipage} &
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
9
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
\(j_{CO_2}\)
\strut\end{minipage} &
\begin{minipage}[t]{0.45\columnwidth}\raggedright\strut
CO\textsubscript{2} input to photosynthesis
\strut\end{minipage} &
\begin{minipage}[t]{0.27\columnwidth}\raggedright\strut

@@

d\textsuperscript{-1}
\strut\end{minipage} &
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
10
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
\(j_L\)
\strut\end{minipage} &
\begin{minipage}[t]{0.45\columnwidth}\raggedright\strut
Light absorption rate
\strut\end{minipage} &
\begin{minipage}[t]{0.27\columnwidth}\raggedright\strut
mol photons C-mol S\textsuperscript{-1} d\textsuperscript{-1}
\strut\end{minipage} &
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
12
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
\(r_{CH}\)
\strut\end{minipage} &
\begin{minipage}[t]{0.45\columnwidth}\raggedright\strut
Recycled CO\textsubscript{2} from host
\strut\end{minipage} &
\begin{minipage}[t]{0.27\columnwidth}\raggedright\strut

@@

d\textsuperscript{-1}
\strut\end{minipage} &
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
13
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
\(r_{CS}\)
\strut\end{minipage} &
\begin{minipage}[t]{0.45\columnwidth}\raggedright\strut
Recycled CO\textsubscript{2} from symbiont
\strut\end{minipage} &
\begin{minipage}[t]{0.27\columnwidth}\raggedright\strut

@@

d\textsuperscript{-1}
\strut\end{minipage} &
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
14
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
\(j_{CP}\)
\strut\end{minipage} &
\begin{minipage}[t]{0.45\columnwidth}\raggedright\strut
Photosynthesis rate
\strut\end{minipage} &
\begin{minipage}[t]{0.27\columnwidth}\raggedright\strut
mol C C-mol S\textsuperscript{-1} d\textsuperscript{-1}
\strut\end{minipage} &
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
15
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
\(j_{eL}\)
\strut\end{minipage} &
\begin{minipage}[t]{0.45\columnwidth}\raggedright\strut
Light energy in excess of photochemistry
\strut\end{minipage} &
\begin{minipage}[t]{0.27\columnwidth}\raggedright\strut
mol photons C-mol S\textsuperscript{-1} d\textsuperscript{-1}
\strut\end{minipage} &
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
16
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
\(j_{NPQ}\)
\strut\end{minipage} &
\begin{minipage}[t]{0.45\columnwidth}\raggedright\strut
Total capacity of NPQ
\strut\end{minipage} &
\begin{minipage}[t]{0.27\columnwidth}\raggedright\strut
mol photons C-mol S\textsuperscript{-1} d\textsuperscript{-1}
\strut\end{minipage} &
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
17
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
\(c_{ROS}\)
\strut\end{minipage} &
\begin{minipage}[t]{0.45\columnwidth}\raggedright\strut
ROS production proportional to baseline
\strut\end{minipage} &
\begin{minipage}[t]{0.27\columnwidth}\raggedright\strut
--
\strut\end{minipage} &
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
18
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
\(r_{NS}\)
\strut\end{minipage} &
\begin{minipage}[t]{0.45\columnwidth}\raggedright\strut
Recycled nitrogen from symbiont turnover
\strut\end{minipage} &
\begin{minipage}[t]{0.27\columnwidth}\raggedright\strut
mol N C-mol S\textsuperscript{-1} d\textsuperscript{-1}
\strut\end{minipage} &
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
19
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
\(j_{SG}\)
\strut\end{minipage} &
\begin{minipage}[t]{0.45\columnwidth}\raggedright\strut
Symbiont biomass formation rate
\strut\end{minipage} &
\begin{minipage}[t]{0.27\columnwidth}\raggedright\strut
C-mol S C-mol S\textsuperscript{-1} d\textsuperscript{-1}
\strut\end{minipage} &
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
20
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
\(\rho_C\)
\strut\end{minipage} &
\begin{minipage}[t]{0.45\columnwidth}\raggedright\strut
Fixed carbon shared with host
\strut\end{minipage} &
\begin{minipage}[t]{0.27\columnwidth}\raggedright\strut
mol C C-mol S\textsuperscript{-1} d\textsuperscript{-1}
\strut\end{minipage} &
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
21
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
\(j_{ST}\)
\strut\end{minipage} &
\begin{minipage}[t]{0.45\columnwidth}\raggedright\strut
Symbiont biomass turnover rate
\strut\end{minipage} &
\begin{minipage}[t]{0.27\columnwidth}\raggedright\strut
C-mol S C-mol S\textsuperscript{-1} d\textsuperscript{-1}
\strut\end{minipage} &
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
22
\strut\end{minipage}\tabularnewline

@@

\begin{minipage}[b]{0.10\columnwidth}\raggedright\strut
Symbol
\strut\end{minipage} &
\begin{minipage}[b]{0.45\columnwidth}\raggedright\strut
Description
\strut\end{minipage} &
\begin{minipage}[b]{0.25\columnwidth}\raggedright\strut
Units
\strut\end{minipage} &
\begin{minipage}[b]{0.12\columnwidth}\raggedright\strut
Value
\strut\end{minipage}\tabularnewline

@@

\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
\(n_{NH}\)
\strut\end{minipage} &
\begin{minipage}[t]{0.45\columnwidth}\raggedright\strut
N:C molar ratio in host biomass
\strut\end{minipage} &
\begin{minipage}[t]{0.25\columnwidth}\raggedright\strut
--
\strut\end{minipage} &
\begin{minipage}[t]{0.12\columnwidth}\raggedright\strut
\(0.18\)
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
\(n_{NS}\)
\strut\end{minipage} &
\begin{minipage}[t]{0.45\columnwidth}\raggedright\strut
N:C molar ratio in symbiont biomass
\strut\end{minipage} &
\begin{minipage}[t]{0.25\columnwidth}\raggedright\strut
--
\strut\end{minipage} &
\begin{minipage}[t]{0.12\columnwidth}\raggedright\strut
\(0.13\)
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
\(n_{NX}\)
\strut\end{minipage} &
\begin{minipage}[t]{0.45\columnwidth}\raggedright\strut
N:C molar ratio in prey biomass
\strut\end{minipage} &
\begin{minipage}[t]{0.25\columnwidth}\raggedright\strut
--
\strut\end{minipage} &
\begin{minipage}[t]{0.12\columnwidth}\raggedright\strut
\(0.2\)
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
\(j_{HT}^0\)
\strut\end{minipage} &
\begin{minipage}[t]{0.45\columnwidth}\raggedright\strut
Maintenance rate of host biomass
\strut\end{minipage} &
\begin{minipage}[t]{0.25\columnwidth}\raggedright\strut
C-mol H C-mol H\textsuperscript{-1} d\textsuperscript{-1}
\strut\end{minipage} &
\begin{minipage}[t]{0.12\columnwidth}\raggedright\strut
\(0.03\)
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
\(j_{ST}^0\)
\strut\end{minipage} &
\begin{minipage}[t]{0.45\columnwidth}\raggedright\strut
Maintenance rate of symbiont biomass
\strut\end{minipage} &
\begin{minipage}[t]{0.25\columnwidth}\raggedright\strut
C-mol S C-mol S\textsuperscript{-1} d\textsuperscript{-1}
\strut\end{minipage} &
\begin{minipage}[t]{0.12\columnwidth}\raggedright\strut
\(0.03\)
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
\(\sigma_{NH}\)
\strut\end{minipage} &
\begin{minipage}[t]{0.45\columnwidth}\raggedright\strut
Proportion N turnover recycled in host
\strut\end{minipage} &
\begin{minipage}[t]{0.25\columnwidth}\raggedright\strut
--
\strut\end{minipage} &
\begin{minipage}[t]{0.12\columnwidth}\raggedright\strut
\(0.9\)
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
\(\sigma_{CH}\)
\strut\end{minipage} &
\begin{minipage}[t]{0.45\columnwidth}\raggedright\strut
Proportion host metabolic CO\textsubscript{2} recycled to photosynthesis
\strut\end{minipage} &
\begin{minipage}[t]{0.25\columnwidth}\raggedright\strut
--

>>>>

  \title{A dynamic bioenergetic model for coral-\emph{Symbiodinium} symbioses and
coral bleaching as an alternate stable state}
    \author[HIMB]{Ross Cunning\corref{c1}}
   \ead{ross.cunning@gmail.com} 
   \cortext[c1]{Corresponding Author}
    \author[UCSB,MSI]{Erik B. Muller}

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \emph{Develop a new module of photo-oxidative stress.} Of primary
  interest to coral biologists and ecologists is symbiosis dysfunction
  under environmental stress, resulting in coral ``bleaching''--the loss
  of algal symbionts from the association (Jokiel and Coles 1977).
  Bleaching is thought to be triggered by photo-oxidative stress in
  \emph{Symbiodinium} (Weis 2008), which has been modeled previously as
  a response to absolute external irradiance (Eynaud, Nisbet, and Muller
  2011). However, this response may also depend on self-shading by other
  symbionts (Enríquez, Méndez, and Iglesias-Prieto 2005),
  CO\textsubscript{2} availability at the site of photosynthesis
  (Wooldridge 2009), and other non-photochemical quenching mechanisms
  (Roth 2014). We incorporate these features into a new photo-oxidative
  stress module linking overreduction of the photosynthetic light
  reactions to downstream impacts of photoinhibition and photodamage.
  Importantly, this formulation introduces a link between
  CO\textsubscript{2}-limitation of photosynthesis and bleaching, and
  potential synergistic roles for heterotrophy and nutrient availability
  in influencing bleaching responses (Wooldridge 2014b)
\item
  \emph{Reduce theoretical and mathematical complexity.} Following the
  logic of Jager, Martin, and Zimmer (2013), we exclude certain features
  of formal DEB theory in order to capture behaviors of interest with
  the simplest possible formulation. Here, we present a model without
  reserves, maturity, or reproduction (see Kooijman 2010). This
  formulation precludes modeling the full life cycle of corals as
  reproduction, larval stages, and metamorphosis are not considered, but
  greatly reduces theoretical complexity and parameter numbers, which is
  advantageous given the relative paucity of data for corals. Moreover,
  dynamics of the symbiosis (i.e., changes in symbiont to host biomass,
  including bleaching and recovery) and coral biomass growth are
  efficiently captured with this simpler formulation, which also
  increases accessibility for biologists and ecologists without
  requiring expertise in DEB theory.
\item
  \emph{Provide well-documented, open source code.} In order to
  facilitate the continued development and application of theoretical
  modeling tools for coral symbioses, we provide access to the model in
  the form of an R package called coRal
  \url{github.com/jrcunning/coRal}, which users may install to run and
  visualize model simulations. With an accessible and modular framework,
  we envision this code base as a resource for further development by
  the scientific community to include additional complexity and
  problem-specific components. We chose R (R Core Team 2014), an open
  source programming language in common use by biologists and
  ecologists, to reach the widest possible audience with this work.
\end{enumerate}

@@

\begin{longtable}[]{@{}llll@{}}

@@

\begin{minipage}[b]{0.09\columnwidth}\raggedright\strut
Symbol\strut
\end{minipage} & \begin{minipage}[b]{0.44\columnwidth}\raggedright\strut
Description\strut
\end{minipage} & \begin{minipage}[b]{0.26\columnwidth}\raggedright\strut
Units\strut
\end{minipage} & \begin{minipage}[b]{0.09\columnwidth}\raggedright\strut
Eq. no.\strut
\end{minipage}\tabularnewline

@@

\begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
\(j_X\)\strut
\end{minipage} & \begin{minipage}[t]{0.44\columnwidth}\raggedright\strut
Prey assimilation (feeding) rate\strut
\end{minipage} & \begin{minipage}[t]{0.26\columnwidth}\raggedright\strut
C-mol X C-mol H\textsuperscript{-1} d\textsuperscript{-1}\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
3\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
\(j_N\)\strut
\end{minipage} & \begin{minipage}[t]{0.44\columnwidth}\raggedright\strut
Nitrogen uptake rate\strut
\end{minipage} & \begin{minipage}[t]{0.26\columnwidth}\raggedright\strut
mol N Cmol H\textsuperscript{-1} d\textsuperscript{-1}\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
4\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
\(j_{HG}\)\strut
\end{minipage} & \begin{minipage}[t]{0.44\columnwidth}\raggedright\strut
Host biomass formation rate\strut
\end{minipage} & \begin{minipage}[t]{0.26\columnwidth}\raggedright\strut
C-mol H C-mol H\textsuperscript{-1} d\textsuperscript{-1}\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
5\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
\(j_{HT}\)\strut
\end{minipage} & \begin{minipage}[t]{0.44\columnwidth}\raggedright\strut
Host biomass turnover rate\strut
\end{minipage} & \begin{minipage}[t]{0.26\columnwidth}\raggedright\strut
C-mol H C-mol H\textsuperscript{-1} d\textsuperscript{-1}\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
6\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
\(r_{NH}\)\strut
\end{minipage} & \begin{minipage}[t]{0.44\columnwidth}\raggedright\strut
Recycled nitrogen from host turnover\strut
\end{minipage} & \begin{minipage}[t]{0.26\columnwidth}\raggedright\strut
mol N C-mol H\textsuperscript{-1} d\textsuperscript{-1}\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
7\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
\(\rho_N\)\strut
\end{minipage} & \begin{minipage}[t]{0.44\columnwidth}\raggedright\strut
Nitrogen shared with the symbiont\strut
\end{minipage} & \begin{minipage}[t]{0.26\columnwidth}\raggedright\strut
mol N C-mol H\textsuperscript{-1} d\textsuperscript{-1}\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
8\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
\(j_{eC}\)\strut
\end{minipage} & \begin{minipage}[t]{0.44\columnwidth}\raggedright\strut
Excess carbon used to activate host CCMs\strut
\end{minipage} & \begin{minipage}[t]{0.26\columnwidth}\raggedright\strut
mol C C-mol H\textsuperscript{-1} d\textsuperscript{-1}\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
9\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
\(j_{CO_2}\)\strut
\end{minipage} & \begin{minipage}[t]{0.44\columnwidth}\raggedright\strut
CO\textsubscript{2} input to photosynthesis\strut
\end{minipage} & \begin{minipage}[t]{0.26\columnwidth}\raggedright\strut

@@

d\textsuperscript{-1}\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
10\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
\(j_L\)\strut
\end{minipage} & \begin{minipage}[t]{0.44\columnwidth}\raggedright\strut
Light absorption rate\strut
\end{minipage} & \begin{minipage}[t]{0.26\columnwidth}\raggedright\strut
mol photons C-mol S\textsuperscript{-1} d\textsuperscript{-1}\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
12\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
\(r_{CH}\)\strut
\end{minipage} & \begin{minipage}[t]{0.44\columnwidth}\raggedright\strut
Recycled CO\textsubscript{2} from host\strut
\end{minipage} & \begin{minipage}[t]{0.26\columnwidth}\raggedright\strut

@@

d\textsuperscript{-1}\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
13\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
\(r_{CS}\)\strut
\end{minipage} & \begin{minipage}[t]{0.44\columnwidth}\raggedright\strut
Recycled CO\textsubscript{2} from symbiont\strut
\end{minipage} & \begin{minipage}[t]{0.26\columnwidth}\raggedright\strut

@@

d\textsuperscript{-1}\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
14\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
\(j_{CP}\)\strut
\end{minipage} & \begin{minipage}[t]{0.44\columnwidth}\raggedright\strut
Photosynthesis rate\strut
\end{minipage} & \begin{minipage}[t]{0.26\columnwidth}\raggedright\strut
mol C C-mol S\textsuperscript{-1} d\textsuperscript{-1}\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
15\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
\(j_{eL}\)\strut
\end{minipage} & \begin{minipage}[t]{0.44\columnwidth}\raggedright\strut
Light energy in excess of photochemistry\strut
\end{minipage} & \begin{minipage}[t]{0.26\columnwidth}\raggedright\strut
mol photons C-mol S\textsuperscript{-1} d\textsuperscript{-1}\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
16\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
\(j_{NPQ}\)\strut
\end{minipage} & \begin{minipage}[t]{0.44\columnwidth}\raggedright\strut
Total capacity of NPQ\strut
\end{minipage} & \begin{minipage}[t]{0.26\columnwidth}\raggedright\strut
mol photons C-mol S\textsuperscript{-1} d\textsuperscript{-1}\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
17\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
\(c_{ROS}\)\strut
\end{minipage} & \begin{minipage}[t]{0.44\columnwidth}\raggedright\strut
ROS production proportional to baseline\strut
\end{minipage} & \begin{minipage}[t]{0.26\columnwidth}\raggedright\strut
--\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
18\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
\(r_{NS}\)\strut
\end{minipage} & \begin{minipage}[t]{0.44\columnwidth}\raggedright\strut
Recycled nitrogen from symbiont turnover\strut
\end{minipage} & \begin{minipage}[t]{0.26\columnwidth}\raggedright\strut
mol N C-mol S\textsuperscript{-1} d\textsuperscript{-1}\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
19\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
\(j_{SG}\)\strut
\end{minipage} & \begin{minipage}[t]{0.44\columnwidth}\raggedright\strut
Symbiont biomass formation rate\strut
\end{minipage} & \begin{minipage}[t]{0.26\columnwidth}\raggedright\strut
C-mol S C-mol S\textsuperscript{-1} d\textsuperscript{-1}\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
20\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
\(\rho_C\)\strut
\end{minipage} & \begin{minipage}[t]{0.44\columnwidth}\raggedright\strut
Fixed carbon shared with host\strut
\end{minipage} & \begin{minipage}[t]{0.26\columnwidth}\raggedright\strut
mol C C-mol S\textsuperscript{-1} d\textsuperscript{-1}\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
21\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
\(j_{ST}\)\strut
\end{minipage} & \begin{minipage}[t]{0.44\columnwidth}\raggedright\strut
Symbiont biomass turnover rate\strut
\end{minipage} & \begin{minipage}[t]{0.26\columnwidth}\raggedright\strut
C-mol S C-mol S\textsuperscript{-1} d\textsuperscript{-1}\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
22\strut
\end{minipage}\tabularnewline

@@

\begin{minipage}[b]{0.09\columnwidth}\raggedright\strut
Symbol\strut
\end{minipage} & \begin{minipage}[b]{0.44\columnwidth}\raggedright\strut
Description\strut
\end{minipage} & \begin{minipage}[b]{0.24\columnwidth}\raggedright\strut
Units\strut
\end{minipage} & \begin{minipage}[b]{0.12\columnwidth}\raggedright\strut
Value\strut
\end{minipage}\tabularnewline

@@

\begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
\(n_{NH}\)\strut
\end{minipage} & \begin{minipage}[t]{0.44\columnwidth}\raggedright\strut
N:C molar ratio in host biomass\strut
\end{minipage} & \begin{minipage}[t]{0.24\columnwidth}\raggedright\strut
--\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\raggedright\strut
\(0.18\)\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
\(n_{NS}\)\strut
\end{minipage} & \begin{minipage}[t]{0.44\columnwidth}\raggedright\strut
N:C molar ratio in symbiont biomass\strut
\end{minipage} & \begin{minipage}[t]{0.24\columnwidth}\raggedright\strut
--\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\raggedright\strut
\(0.13\)\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
\(n_{NX}\)\strut
\end{minipage} & \begin{minipage}[t]{0.44\columnwidth}\raggedright\strut
N:C molar ratio in prey biomass\strut
\end{minipage} & \begin{minipage}[t]{0.24\columnwidth}\raggedright\strut
--\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\raggedright\strut
\(0.2\)\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
\(j_{HT}^0\)\strut
\end{minipage} & \begin{minipage}[t]{0.44\columnwidth}\raggedright\strut
Maintenance rate of host biomass\strut
\end{minipage} & \begin{minipage}[t]{0.24\columnwidth}\raggedright\strut
C-mol H C-mol H\textsuperscript{-1} d\textsuperscript{-1}\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\raggedright\strut
\(0.03\)\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
\(j_{ST}^0\)\strut
\end{minipage} & \begin{minipage}[t]{0.44\columnwidth}\raggedright\strut
Maintenance rate of symbiont biomass\strut
\end{minipage} & \begin{minipage}[t]{0.24\columnwidth}\raggedright\strut
C-mol S C-mol S\textsuperscript{-1} d\textsuperscript{-1}\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\raggedright\strut
\(0.03\)\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
\(\sigma_{NH}\)\strut
\end{minipage} & \begin{minipage}[t]{0.44\columnwidth}\raggedright\strut
Proportion N turnover recycled in host\strut
\end{minipage} & \begin{minipage}[t]{0.24\columnwidth}\raggedright\strut
--\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\raggedright\strut
\(0.9\)\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
\(\sigma_{CH}\)\strut
\end{minipage} & \begin{minipage}[t]{0.44\columnwidth}\raggedright\strut
Proportion host metabolic CO\textsubscript{2} recycled to
photosynthesis\strut
\end{minipage} & \begin{minipage}[t]{0.24\columnwidth}\raggedright\strut
--\strut
